\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}

\title{CSC111 Winter 2024 Project 1}
\author{Kathleen Wang, Yanting Fan}
\date{\today}

\begin{document}
\maketitle

\section*{Enhancements}


\begin{enumerate}

\item Describe your enhancement \#1 here
	\begin{itemize}
	\item Brief description of what the enhancement is:
        \item \('\)open' command
        \item Opens the backpack when backpack is in player's inventory.
	\item Complexity level (choose from low/medium/high): low
	\item Reasons you believe this is the complexity level (e.g.mention implementation details, how much code did you have to add/change from the baseline, what challenges did you face, etc.):
        \item We added a \('\)open\_backpack' function under the World class.
        \item In order to get the pen, the player has to first pick up the backpack at the designed location - Robarts Commons (location number 13).
        \item Then, the player can choose to open the backpack at any time to get the lucky pen.
        \item Once the player enter \('\)open', the backpack will get dropped from the inventory and lucky pen will be added.
	\end{itemize}


\item Describe your enhancement \#2 here
	\begin{itemize}
	\item Basic description of what the enhancement is:
        \item \('\)say hi' command
        \item Greets Sadia and print out a conversation between the player and Sadia.
        \item Sadia then write a cheatsheet for the player and it will be added to player's inventory automatically.
	\item Complexity level (low/medium/high): low
	\item Reasons you believe this is the complexity level (e.g.mention implementation details):
        \item We added an extra two lines in the \('\)available\_actions' function under the World class.
        \item The \('\)say hi' command will show up in the list of actions if and only if the player is at BA 4290 and hasn't gotten a cheatsheet from Sadia.
	\end{itemize}


\item Describe your enhancement \#3 here
	\begin{itemize}
	\item Basic description of what the enhancement is:
        \item The player is only allowed to enter the Robarts Library with a T-card.
	\item Complexity level (low/medium/high): medium
	\item Reasons you believe this is the complexity level (e.g.mention implementation details):
        \item We added 4 lines in the \('\)adventure.py' to check if T-card is in player's inventory.
        \item We added another function \('\)undo\_actions' that undo the player's most recent move .
        \item If not, then the player's x, y coordinates will be returned to the most recent move based on the implementation of the \('\)undo\_actions' function.
	\end{itemize}

\end{enumerate}


\section*{Extra Gameplay Files}

If you have any extra \texttt{gameplay\#.txt} files, describe them below.
    In \texttt{gameplay\#1.txt}, the player will first visit Robarts Commons with T-card. 
    Then, they open the backpack to pick up the lucky pen. 
    After that, they will visit Bahen Centre and enter room 4290 to get a cheatsheet from Sadia.
    Finally, they will head to EX100 to take their final.

\end{document}
